### 2019-09-05 tables/03_model_summary.Rmd
rm row names

options(knitr.kable.NA = "-")  
dt %>%
  # dplyr::filter(str_detect(response, "tp")) %>%
  # dplyr::select(-response) %>%
  dplyr::rename("$R^2$" = r2) %>%
  knitr::kable(digits = 2, format = "markdown", caption = "TP Model R2")
```

>>>>

options(knitr.kable.NA = "-")  
dt %>%
  # dplyr::filter(str_detect(response, "tp")) %>%
  # dplyr::select(-response) %>%
  dplyr::rename("$R^2$" = r2) %>%
  knitr::kable(digits = 2, format = "markdown", caption = "TP Model R2", 
               row.names = FALSE)
```
